
---
output: # rmarkdown::github_document
  html_document:
    theme: cerulean
    toc: true
  pdf_document: default
  word_document: default
title: "Assignment 5: Handle Missing Values"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment5.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**The data:** 

This assignment works with the Adult Census Data that can be downloaded at [this link.](https://bryantstats.github.io/math421/data/adult_census_missing.csv)

-------

**Questions**

1. Use `read_csv` to import the data.  Show the number of NAs for each columns.   
```{r}
library(tidyverse)
adult <- read_csv('C:/Users/student/Documents/MATH421/Marco-Loccisano.github.io/adult_census_missing.csv')
colSums(is.na(adult))
```

2. Using function `aggr` the VIM package to plot the number of NAs for each column. 
```{r}
library(VIM)
aggr(adult)
```

3. Find other forms of missing values. Hint: You can use the `table` function to check if there are suspicious categories (Unknown, for example) in a variable. What all other forms of missing values shown in the data. 
```{r}
table(adult$age)
table(adult$workclass)
table(adult$education.num)
table(adult$education)
table(adult$marital.status)
table(adult$occupation)
table(adult$sex)
table(adult$capital.gain)
table(adult$native.country)
table(adult$race)
table(adult$relationship)
table(adult$hours.per.week)

```
?, Not known, and Unknown are different suspicious categories
4. Replace all the forms of missing values found to NA
```{r}
adult <- na_if(adult, 'Unknown')
adult <- na_if(adult, 'Not Known')
adult <- na_if(adult, '?')
adult <- na_if(adult, '99999')
```

5. Replot the number of NAs for each column. 
```{r}
aggr(adult)
```

6. Approach 1 to handle NAs: remove all rows that have any NAs. Save the dataset after removing as a different data. The original data is unchanged (still have NAs).  How many rows left after removing?
```{r}
adult2 <- drop_na(adult)
```
29717 rows
7. Approach 2 to handle NAs:  Fill all the NAs with the previous or next value. (Hint: Using `fill` function).  Save the dataset after filling as a different data. The original data is unchanged (still have NAs). 
```{r}
adult3 <- adult %>% fill(age, workclass, education, marital.status, occupation, sex, capital.gain, native.country, relationship, .direction = 'updown')
```

8. Approach 3 to handle NAs: For numeric variable, replace the NAs by the median.  For categorical variables, replace the NAs to the majority. 
```{r}
adult4 <- adult
mean_age <- mean(adult$age, na.rm=TRUE)
adult4$age <- replace_na(adult$age, mean_age)

mean_fnlwgt <- mean(adult$fnlwgt, na.rm=TRUE)
adult4$fnlwgt <- replace_na(adult$fnlwgt, mean_fnlwgt)

mean_capital.gain <- mean(adult$capital.gain, na.rm=TRUE)
adult4$capital.gain <- replace_na(adult$capital.gain, mean_capital.gain)

majority_sex <- names(which.max(table(adult$sex)))
adult4$sex <- replace_na(adult$sex, majority_sex)

majority_workclass <- names(which.max(table(adult$workclass)))
adult4$workclass <- replace_na(adult$workclass, majority_workclass)

majority_education <- names(which.max(table(adult$education)))
adult4$education <- replace_na(adult$sex, majority_education)

majority_marital.status <- names(which.max(table(adult$marital.status)))
adult4$marital.status <- replace_na(adult$sex, majority_marital.status)

majority_occupation <- names(which.max(table(adult$occupation)))
adult4$occupation <- replace_na(adult$sex, majority_occupation)

majority_relationship <- names(which.max(table(adult$relationship)))
adult4$relationship <- replace_na(adult$relationship, majority_relationship)
```





