
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

**Notice:** *In this assignment, all the plot should have title, caption, and axis labels. *

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 

Hint: 

-  Use `filter` to select the most current date 

-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths
```{r}
library(tidyverse)
df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
df %>% filter(Date_reported>='2022-10-18') %>% mutate(rank = rank(-Cumulative_deaths)) %>% filter(rank<=3)

```


2. Use `transition_reveal` to make a plot revealing the number of deaths in the three countries with the most numbers of deaths
```{r}
library(gganimate)
library(ggplot2)
library(tidyverse)
library(lubridate)
df %>% 
  filter(Country_code== 'BR'|Country_code=='IN'|Country_code=='US') %>% 
  ggplot(aes(x=Date_reported, y=Cumulative_deaths,color = Country_code))+ 
  geom_line()+
  transition_reveal(Date_reported)
```

3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 
```{r}
df <- df %>% mutate(death_per_cases=Cumulative_deaths/Cumulative_cases)
df  %>% group_by(Country_code) %>%filter(death_per_cases!= 'NaN'&death_per_cases!='Inf') %>%  summarize(max_death_per_cases=max(death_per_cases)) %>% mutate(rank = rank(-max_death_per_cases)) %>% filter(rank<=5) %>% arrange(rank)
```

4. Use `transition_reveal` to make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 
```{r}
df %>% 
  filter(Country_code== 'IT'|Country_code=='MX'|Country_code=='US') %>% 
  ggplot(aes(x=Date_reported, y=death_per_cases,color = Country_code))+ 
  geom_line()+
  transition_reveal(Date_reported)
```

5. Import the following data https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv
                      
Use `transition_reveal` to plot the total vaccinations per hundred by level of income. Hint: the levels of income are identified in the `location` variable. Put a short comment on the caption of the plot. 
```{r}
df <- read_csv('https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv')
table(df$location)
df  %>% filter(location=='Low income'|location=='Lower middle income'|location=='Upper middle income'|location=='High income') %>% 
  ggplot(aes(x=date, y=total_vaccinations_per_hundred,color = location))+ 
  geom_line()+
  transition_reveal(date)
```

