---
title: "assignment 3 extra credit"
author: "Marco Loccisano"
date: "2022-09-28"
output: html_document
---

16.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when
```{r}
adult <- read.csv('C:/Users/student/Documents/MATH421/Marco-Loccisano.github.io/adult_census.csv')
library(lubridate)
library(dplyr)
head(adult, 5)
str(adult)
names(adult)
mean(adult$age, na.rm=TRUE)
min(adult$age, na.rm=TRUE)
max(adult$age, na.rm=TRUE)
table(adult$education)
sum(is.na(adult$age))
colSums(is.na(adult))
class(adult$age)
cor(adult$education.num, adult$hours.per.week)
by(adult$age, adult$sex, mean)
adult$age2 <- ifelse(adult$age<=30,
                   'Young','Old')
adult$hours.per.week2 <- case_when(adult$hours.per.week <= 20 ~ 'Part-Time',
                                adult$hours.per.week > 20 & adult$hours.per.week <= 40 ~ 'Full-Time',
                                adult$hours.per.week > 40 ~ 'Overtime')
```


17. In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

```{r}
adult$age2 <- ifelse(adult$age<=30,
                   'Young','Old')
adult$race2 <- ifelse(adult$race == 'White','White','Not_White')
```

